### 2019-01-08 writing/thesis/chapters/results.tex
Some proof changes.

\begin{figure}[htb]
  \centering
  \includegraphics{thesis_convergence}
  \caption{$L_2$-Error vs.\ Grid Size}
  \label{fig:convergence-l2-error}
\end{figure}

@@

\todo{Describe how to integrate the error for cells, and effect of volume}
We evaluate the cell-wise error with Gaussian quadrature using \cref{eq:integration-by-substitution}
 \begin{equation}
   \Vert f_K(x) \Vert_p = \left( V \sum_{\bm{i}} \vert f(\bm{x}_i, t) - \hat{f}(\bm{x}_i, t) \vert^p w_{{\bm{i}}}  \right)^{1/p},
 \end{equation}
where $V = \Delta x \Delta y$ is the volume of each two-dimensional cell.
The sum runs over all quadrature nodes $x_i$ with weights $w_i$.
We use ten nodes.

>>>>

\begin{figure}[htb]
  \centering
  \includegraphics{thesis_convergence}
  \caption{$L_2$-Error vs.\ Grid Size.
    The dashed lines are the optimal order of convergence $N+1$.
  The line is estimated by using the constant part of a linear regression fit and the ideal order as slope.}
  \label{fig:convergence-l2-error}
\end{figure}

@@

\todo{Describe how to integrate the error for cells, and effect of volume}
We evaluate the cell-wise error with Gaussian quadrature using \cref{eq:integration-by-substitution}
 \begin{equation}
   \Vert f_K(x) \Vert_p = \left( V \sum_{\bm{i}} \vert f(\bm{x}_i, t) - \hat{f}(\bm{x}_i, t) \vert^p w_{{\bm{i}}}  \right)^{1/p},
 \end{equation}
where $V = \Delta x \Delta y$ is the volume of each two-dimensional cell.
\todo{Use quadNodes, quadWeights and volume macro}
The sum runs over all quadrature nodes $x_i$ with weights $w_i$.
We use ten nodes for all orders and evaluate our solution for all nodes.
In this way we ensure a fair comparision.
